Implicit spatial model to krill Dynamic Population in Antarctic Peninsula, 48-1 SubArea. SS3 aplications

### 2024-03-27 Run_SS3_Krill_481.Rmd
commit pdf

# 
# install.packages("caTools")
# library("caTools")
# 
# install.packages("r4ss")
library(r4ss)
library(here)
#remotes::install_github("PIFSCstockassessments/ss3diags")
library(ss3diags)
library(kableExtra)
```

@@

```{r}
SSplotData(base.model01, subplot = 1, 
           fleetnames = c("Fishery", "Survey", "Predator"),
           fleetcol = c(7,6, 4))

@@

```{r eval=TRUE}
SSplotRunstest(base.model2, 
               subplots = "cpue",
               add=T)
SSplotRunstest(base.model2, 
               subplots = "len",
               add=T)
```

@@

```{r}
retroModels <- SSgetoutput(dirvec=file.path(dir2,
                                            "Retrospective",
                                            paste("retro",0:-5,
                                                  sep="")))

retroSummary <- SSsummarize(retroModels)
```

```{r}
#save(retroSummary, retroModels, file="retro5.Rdata")

retro01 <- SSplotRetro(retroSummary,
            add=T,
            forecast = F,
            legend = F,
            verbose=F)
retro2 <- SSplotRetro(retroSummary,
            add=T,
            forecast = F,
            legend = F,
            verbose=F)
retro1 <- SSplotRetro(retroSummary,
            add=T,
            forecast = F,
            legend = F,
            verbose=F)

retro7 <- SSplotRetro(retroSummary,
            add=T,
            forecast = F,
            legend = F,
            verbose=F,
            legendlabels="default")
```
## Hindcast Cross-Validation and prediction skill

@@

```{r}
hci = SSplotHCxval(retroSummary, 
                   add = T, 
                   verbose = F, 
                   legendcex = 0.7)
```
## Kobe (status)

@@

```{r}
SShcbias(retroSummary,quant="SSB",verbose=F)
SShcbias(retroSummary,quant="F",verbose=F)
```

@@

```{r eval=FALSE, echo= FALSE}
# 1. Identificar el directorio donde se encuentra el modelo base ----
dirname.model.run <- here("s10")

@@

dirname.R0.profile <- here("Ejercicios","Perfil_Verosimilitud")
dir.create(path=dirname.R0.profile, showWarnings = TRUE, recursive = TRUE)

@@

plotdir=paste0(dirname.R0.profile, "/plots_Verosimilitud")
dir.create(path=plotdir, showWarnings = TRUE, recursive = TRUE)

@@

reference.dir <- paste0(dirname.R0.profile,'/simple') 
dir.create(path=reference.dir, showWarnings = TRUE, recursive = TRUE)

@@

file.copy(Sys.glob(paste(dirname.model.run, "*.*", sep="/"),
                   dirmark = FALSE),
                    reference.dir)

@@

copy_SS_inputs(dir.old = reference.dir, 
               dir.new =  dirname.R0.profile,
               copy_exe = TRUE,
               verbose = FALSE)

@@

R0.vec <- seq(7,11,0.5)  
Nprof.R0 <- length(R0.vec)

@@

?SS_profile()
profile <- profile(dir="dir10", # directory
                      model="ss_osx",
                      oldctlfile ="control.ss",
                      newctlfile="control_modified.ss",
                      string="SR_LN(R0)",
                      profilevec=R0.vec)

# 16. Leer los archivos de salida ----
# (con nombres como Report1.sso, Report2.sso, etc.)
prof.R0.models <- SSgetoutput(dirvec=dirname.R0.profile, 
                              keyvec=1:Nprof.R0, 
                              getcovar = FALSE)

# 17. Resumir las salidas con la función SSsummarize()  ----
prof.R0.summary <- SSsummarize(prof.R0.models)

# 18. Identificar los componentes de Verosimilitud ----
mainlike_components         <- c('TOTAL',"Survey", 'Length_comp',"Age_comp",'Size_at_age','Recruitment') 
mainlike_components_labels  <- c('Total likelihood','Index likelihood','Length likelihood',"Age likelihood",'Size_at_age likelihood','Recruitment likelihood')

# 19. Funciones para generar plots de perfil de verosimilitud ----
### SSplotProfile() ----
png(file.path(plotdir,"R0_profile_plot.png"),width=7,height=4.5,res=300,units='in')
par(mar=c(5,4,1,1))

SSplotProfile(prof.R0.summary,           # summary object
              profile.string = "R0",     # substring of profile parameter
              profile.label=expression(log(italic(R)[0])), ymax=150,minfraction = 0.001,
              pheight=4.5, 
              print=FALSE, 
              plotdir=plotdir, 
              components = mainlike_components, 
              component.labels = mainlike_components_labels,
              add_cutoff = TRUE,
              cutoff_prob = 0.95)

@@

### SSplotComparisons() ----
# Comparación de series de tiempo 
labs <- paste("SR_Ln(R0) = ",R0.vec)
labs[which(round(R0.vec,2)==Baseval)] <- paste("SR_Ln(R0) = ",Baseval,"(Base model)")

@@

### PinerPlot() ----
#### R0_profile_plot_Length_like ----
png(file.path(plotdir,"R0_profile_plot_Length_like.png"),width=7,height=4.5,res=300,units='in')
par(mar=c(5,4,1,1))
PinerPlot(prof.R0.summary, 
          profile.string = "R0", 
          component = "Length_like",
          main = "Changes in length-composition likelihoods by fleet",
          add_cutoff = TRUE,
          cutoff_prob = 0.95)
Baseval <- round(Base$parameters$Value[grep("SR_LN",
                                      Base$parameters$Label)],2)
Baselab <- paste(Baseval,sep="")
axis(1,at=Baseval,
     label=Baselab)
abline(v = Baseval, lty=2)
dev.off()
#### R0_profile_plot_Survey_like ----
png(file.path(plotdir,"R0_profile_plot_Survey_like.png"),width=7,height=4.5,res=300,units='in')
par(mar=c(5,4,1,1))
PinerPlot(prof.R0.summary, profile.string = "R0", component = "Surv_like",main = "Changes in Index likelihoods by fleet",
          add_cutoff = TRUE,
          cutoff_prob = 0.95, legendloc="topleft")
Baseval <- round(Base$parameters$Value[grep("SR_LN",Base$parameters$Label)],2)
Baselab <- paste(Baseval,sep="")
axis(1,at=Baseval,label=Baselab)
abline(v = Baseval, lty=2)
dev.off()
```

@@

```{r}
#PLOT labels, name of each model run
legend.labels <- c( "s01",
                  "s1",
                 "s2",
                 "s3",
                 "s4",
                 "s5",
                 "s6",
                 "s7")

@@

SSplotComparisons(summaryoutput,
                  legendlabels = c("s01",
                                   "s1",
                                   "s2",
                 "s3",
                 "s4",
                 "s5",
                 "s6",
                 "s7"),
                 labels = c("Year", 
                            "Spawning biomass (t)",
                            "Relative spawning biomass", 
                            "Age-0 recruits (1,000s)",
                            "Recruitment deviations", 
                            "Index", "Log index", 
                            "1 - SPR", 
                            "Density",
                            "Management target", 
                            "Minimum stock size threshold",
                            "Spawning output",
                            "Harvest rate"))
```

>>>>

# 
# install.packages("caTools")
# library("caTools")
# 
# install.packages("r4ss")
library(r4ss)
library(here)
#remotes::install_github("PIFSCstockassessments/ss3diags")
library(ss3diags)
library(kableExtra)
library(doParallel) # facilita la ejecución paralela en R
detectCores()
registerDoParallel(8)
library(ggpubr)
```

@@

```{r}
SSplotData(base.model01, subplot = 1, 
           fleetnames = c("Fishery", "Survey", "Predator"),
           fleetcol = c("blue","green", "red"))

@@

```{r eval=TRUE}
SSplotRunstest(base.model01, 
               subplots = "cpue",
               add=T)
SSplotRunstest(base.model2, 
               subplots = "len",
               add=T)
```

@@

```{r echo=FALSE}
#s01
retroModels01 <- SSgetoutput(dirvec=file.path(dir01,
                                            "Retrospective",
                                            paste("retro",0:-5,
                                                  sep="")))

retroSummary01 <- SSsummarize(retroModels01)
# s1
retroModels1 <- SSgetoutput(dirvec=file.path(dir1,
                                            "Retrospective",
                                            paste("retro",0:-5,
                                                  sep="")))

retroSummary1 <- SSsummarize(retroModels1)
#s2
retroModels2 <- SSgetoutput(dirvec=file.path(dir2,
                                            "Retrospective",
                                            paste("retro",0:-5,
                                                  sep="")))

retroSummary2 <- SSsummarize(retroModels2)
#s3
retroModels3 <- SSgetoutput(dirvec=file.path(dir3,
                                            "Retrospective",
                                            paste("retro",0:-5,
                                                  sep="")))

retroSummary3 <- SSsummarize(retroModels3)
#s4
retroModels4 <- SSgetoutput(dirvec=file.path(dir4,
                                            "Retrospective",
                                            paste("retro",0:-5,
                                                  sep="")))

retroSummary4 <- SSsummarize(retroModels4)
#s5
retroModels5 <- SSgetoutput(dirvec=file.path(dir5,
                                            "Retrospective",
                                            paste("retro",0:-5,
                                                  sep="")))

retroSummary5 <- SSsummarize(retroModels5)
#s6
retroModels6 <- SSgetoutput(dirvec=file.path(dir6,
                                            "Retrospective",
                                            paste("retro",0:-5,
                                                  sep="")))

retroSummary6 <- SSsummarize(retroModels6)
#s7
retroModels7 <- SSgetoutput(dirvec=file.path(dir7,
                                            "Retrospective",
                                            paste("retro",0:-5,
                                                  sep="")))

retroSummary7 <- SSsummarize(retroModels7)

```{r echo FALSE}
#save(retroSummary, retroModels, file="retro5.Rdata")

retro01 <- SSplotRetro(retroSummary01,
            add=T,
            forecast = F,
            legend = T,
            verbose=F)
retro1 <- SSplotRetro(retroSummary1,
            add=T,
            forecast = F,
            legend = T,
            verbose=F)
retro2 <- SSplotRetro(retroSummary2,
            add=T,
            forecast = F,
            legend = T,
            verbose=F)
retro3 <- SSplotRetro(retroSummary3,
            add=T,
            forecast = F,
            legend = T,
            verbose=F)
retro4 <- SSplotRetro(retroSummary4,
            add=T,
            forecast = F,
            legend = T,
            verbose=F)
retro5 <- SSplotRetro(retroSummary5,
            add=T,
            forecast = F,
            legend = T,
            verbose=F)

retro6 <- SSplotRetro(retroSummary6,
            add=T,
            forecast = F,
            legend = T,
            verbose=F)

retro7 <- SSplotRetro(retroSummary7,
            add=T,
            forecast = F,
            legend = T,
            verbose=F)
```
```{r echo=FALSE}
ggarrange(retro01,
          retro1,
          retro2,
          retro3,
          retro4,
          retro5,
          retro6,
          retro7, ncol = 4, nrow = 4)
```

## Hindcast Cross-Validation and prediction skill

@@

```{r}
hci = SSplotHCxval(retroSummary2, 
                   add = T, 
                   verbose = F, 
                   legendcex = 0.7)
```
## Kobe (status)

@@

mvln = SSdeltaMVLN(base.model2,
                   Fref = "MSY", 
                   plot = TRUE,
                   addprj=TRUE,
                   virgin = TRUE,
                   mc=100)
```

```{r echo=FALSE}
# model01
tablebias01 <- SShcbias(retroSummary01,quant="SSB",verbose=F)
tablebias02 <- SShcbias(retroSummary01,quant="F",verbose=F)

kbl(tablebias01, booktabs = T,format = "latex",
    caption = "Rho parameter in SSB model s01")  %>% 
    kable_styling(latex_options = "HOLD_position")

kbl(tablebias02, booktabs = T,format = "latex",
    caption = "Rho parameter in F model s01")  %>% 
    kable_styling(latex_options = "HOLD_position")

# model2
tablebias1 <- SShcbias(retroSummary2,quant="SSB",verbose=F)
tablebias2 <- SShcbias(retroSummary2,quant="F",verbose=F)

kbl(tablebias1, booktabs = T,format = "latex",
    caption = "Rho parameter in SSB model s2")  %>% 
    kable_styling(latex_options = "HOLD_position")

kbl(tablebias2, booktabs = T,format = "latex",
    caption = "Rho parameter in F model s2")  %>% 
    kable_styling(latex_options = "HOLD_position")
```

@@

```{r eval=FALSE, echo = FALSE}
# 1. Identificar el directorio donde se encuentra el modelo base ----
dirname.model.run <- here("s2")

@@

dirname.R0.profile <- here("Ejercicios","Perfil_Verosimilitud")
dir.create(path=dirname.R0.profile, showWarnings = TRUE, recursive = TRUE)

@@

plotdir=paste0(dirname.R0.profile, "/plots_Verosimilitud")
dir.create(path=plotdir, showWarnings = TRUE, recursive = TRUE)

@@

reference.dir <- paste0(dirname.R0.profile,'/simple') 
dir.create(path=reference.dir, showWarnings = TRUE, recursive = TRUE)

@@

file.copy(Sys.glob(paste(dirname.model.run, "*.*", sep="/"),
                   dirmark = FALSE),
                    reference.dir)

@@

copy_SS_inputs(dir.old = reference.dir, 
               dir.new =  dirname.R0.profile,
               copy_exe = TRUE,
               verbose = FALSE)

@@

R0.vec <- seq(15,20,0.5)  
Nprof.R0 <- length(R0.vec)

@@

?SS_profile()
profile <- profile(dir=dirname.R0.profile, # directory
                      exe="ss_osx",
                      oldctlfile ="control.ss",
                      newctlfile="control_modified.ss",
                      string="SR_LN(R0)",
                      profilevec=R0.vec)
# 16. Leer los archivos de salida ----
# (con nombres como Report1.sso, Report2.sso, etc.)
prof.R0.models <- SSgetoutput(dirvec=dirname.R0.profile, 
                              keyvec=1:Nprof.R0, 
                              getcovar = FALSE) 
# 17. Resumir las salidas con la función SSsummarize()  ----
prof.R0.summary <- SSsummarize(prof.R0.models)
# 18. Identificar los componentes de Verosimilitud ----
mainlike_components         <- c('TOTAL',
                                 "Survey", 
                                 'Length_comp',
                                 "Age_comp",
                                 'Size_at_age',
                                 'Recruitment') 
mainlike_components_labels  <- c('Total likelihood',
                                 'Index likelihood',
                                 'Length likelihood',
                                 "Age likelihood",
                                 'Size_at_age likelihood',
                                 'Recruitment likelihood') 
# 19. Funciones para generar plots de perfil de verosimilitud ----
### SSplotProfile() ----
png(file.path(plotdir,"R0_profile_plot.png"),
    width=7,
    height=4.5,
    res=300,
    units='in')
par(mar=c(5,4,1,1))
SSplotProfile(prof.R0.summary,           # summary object
              profile.string = "R0",     # substring of profile parameter
              profile.label=expression(log(italic(R)[0])), 
              ymax=150,minfraction = 0.001,
              pheight=4.5, 
              print=FALSE, 
              plotdir=plotdir, 
              components = mainlike_components, 
              component.labels = mainlike_components_labels,
              add_cutoff = TRUE,
              cutoff_prob = 0.95)

@@

### SSplotComparisons() ----
# Comparación de series de tiempo 
labs <- paste("SR_Ln(R0) = ",R0.vec)
labs[which(round(R0.vec,2)==Baseval)] <- paste("SR_Ln(R0) = ",
                                               Baseval,"(Base model)")

@@

### PinerPlot() ----
#### R0_profile_plot_Length_like ----
png(file.path(plotdir,"R0_profile_plot_Length_like.png"),
    width=7,
    height=4.5,
    res=300,
    units='in')
par(mar=c(5,4,1,1))
PinerPlot(prof.R0.summary, 
          profile.string = "R0", 
          component = "Length_like",
          main = "Changes in length-composition likelihoods by fleet",
          add_cutoff = TRUE,
          cutoff_prob = 0.95)
Baseval <- round(Base$parameters$Value[grep("SR_LN",
                                      Base$parameters$Label)],2)
Baselab <- paste(Baseval,sep="")
axis(1,at=Baseval,
     label=Baselab)
abline(v = Baseval, lty=2)
dev.off()
#### R0_profile_plot_Survey_like ----
png(file.path(plotdir,"R0_profile_plot_Survey_like.png"),
    width=7,
    height=4.5,
    res=300,
    units='in')
par(mar=c(5,4,1,1))
PinerPlot(prof.R0.summary, 
          profile.string = "R0", 
          component = "Surv_like",
          main = "Changes in Index likelihoods by fleet",
          add_cutoff = TRUE,
          cutoff_prob = 0.95, legendloc="topleft")
Baseval <- round(Base$parameters$Value[grep("SR_LN",
                                            Base$parameters$Label)],2)
Baselab <- paste(Baseval,sep="")
axis(1,at=Baseval,label=Baselab)
abline(v = Baseval, lty=2)
dev.off()
```

@@

```{r echo=FALSE}
#PLOT labels, name of each model run
legend.labels <- c( "s01",
                  "s1",
                 "s2",
                 "s3",
                 "s4",
                 "s5",
                 "s6",
                 "s7")

@@

SSplotComparisons(summaryoutput,
                  legendlabels = c("s01",
                                   "s1",
                                   "s2",
                 "s3",
                 "s4",
                 "s5",
                 "s6",
                 "s7"),
                 labels = c("Year", 
                            "Spawning biomass (t)",
                            "Relative spawning biomass", 
                            "Age-0 recruits (1,000s)",
                            "Recruitment deviations", 
                            "Index", "Log index", 
                            "1 - SPR", 
                            "Density",
                            "Management target", 
                            "Minimum stock size threshold",
                            "Spawning output",
                            "Harvest rate"))

comp <- SSplotComparisons(summaryoutput,
                  legendlabels = c("s01",
                                   "s1",
                                   "s2",
                 "s3",
                 "s4",
                 "s5",
                 "s6",
                 "s7"),
                 subplots = c(2, 16))
comp
```
